---
title: The Whole Game
author: David Kane
tutorial:
  id: the-whole-game
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: 'Tutorial for Chapter 1: The Whole Game'
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(devtools)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

## Introduction
### 

This tutorial covers [Chapter 1: The Whole Game](https://r-pkgs.org/whole-game.html) from [*R Packages (2e)*](https://r-pkgs.org/) by [Hadley Wickham](https://hadley.nz/) and [Jennifer Bryan](https://jennybryan.org/). [**devtools**](https://devtools.r-lib.org/) is a package designed to make package development easier by providing R functions that simplify and expedite common tasks.




## Summary
### 

This tutorial covered [Chapter 1: The Whole Game](https://r-pkgs.org/whole-game.html) from [*R Packages (2e)*](https://r-pkgs.org/) by [Hadley Wickham](https://hadley.nz/) and [Jennifer Bryan](https://jennybryan.org/). [**devtools**](https://devtools.r-lib.org/) is a package designed to make package development easier by providing R functions that simplify and expedite common tasks.
 

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
